---
title: "Coding Exercises"
author: "Taylor Bennett"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
source("Setup.R")
```

```{r}
data("knz_bison")
```

1.  Create a new column in the bison dataset that calculates the individual's age at the time of observation.

    ```{r}
    #rec_year - animal_yob


    a=knz_bison$rec_year
     
    b=knz_bison$animal_yob

    obs_age <- a-b
     
    print(obs_age) 
    ```

    ```{r}
    bison_age <- knz_bison %>%
      add_column(obs_age)
    bison_age
    ```

2.  Write a function that will first filter the bison dataset based on any user-specified weight threshold (returning the filtered dataset).

    ```{r}
    # specifying weight threshold
    bison_age %>% 
      summarize(weight_avg = mean(animal_weight, na.rm = TRUE))
    ```

```{r}
# I will round to 750 as the threshold
bison_age_size <- mutate(bison_age, size_group = if_else(animal_weight > 750, paste0("large"), paste0("small")))

bison_age_size
```

```{r}
filter_bison <- function(x) {
  x <- animal_weight
  filtered <- mutate(if_else(bison_age_size, x > 750, "large", "small"))
  print(filtered)
}
```

3.  Create a boxplot showing weight distribution between male and female bison, and then conduct a t-test to see if weight is significantly difference between males and females.

    ```{r}
    bison_age_size %>%
      ggplot(aes(x = animal_sex, y = animal_weight)) +   
      geom_boxplot()
    ```

```{r}
bison_age_size %>% 
  t_test(animal_weight ~ animal_sex, var.equal = FALSE, detailed = TRUE) 
```
